### 2021-03-11 Rmd/PPCA_plot_1.Rmd
Edits

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=6, fig.width=16}

@@

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
  dat$Nectar[dat$Nectar=="no"] <- "Absence"
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("#fc2847", "#1cac78"))

@@

#all_spp(PC)

#############################################################################################################################################################

#CALL the output PC for simplicity
PC <- phyl_pca_forest_nectar
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots

nectar_subset <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Nectar <- dat_cleaning_5_nectar$Nectar_presence_absence
  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
  dat$Nectar[dat$Nectar=="no"] <- "Absence"
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("#fc2847", "#1cac78"))
  # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height", "Nectar")

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(6,5.35,5,6,6,6,6)), y = -(PCAloadings$PC2*c(5.75,5,4.75,5.75,5.8,5.5,6)),
                          label = PCAloadings$Variables, color="black",size=5)

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.08, 0.11)) +ggtitle("")

library(cowplot)
 plot_grid(all_spp(phyl_pca_forest),nectar_subset(phyl_pca_forest_nectar), ncol=2,  align = "h")

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=9, fig.width=9}

@@

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
  dat$Nectar[dat$Nectar=="no"] <- "Absence"
   dat$Nectar <- factor(dat$Nectar, levels = c("Presence","Absence"))
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("grey", "black"))

@@

all_spp(PC)

### 2021-03-11 Scripts/7_1_Plot_Model_Output_for_Publication/6_Model_output_plot.Rmd
Edits

setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github
m_5_clust_zero_neg_hclust <- readRDS("m_5_clust_zero_neg_hclust_1.RDS")
setwd("~/R_Projects/Reproductive Traits")
d_5_1 <- read.csv("Data/Csv/d_5_1_brms_all_5_clusters.csv")
#Visits
ce_1 <- conditional_effects(m_5_clust_zero_neg_hclust, effects = "Clusters:guild",points=T) 
#change colnames in model output to use same aesthetics
#if not gg seems to don't like it
colnames(ce_1[[1]])[4] <- "a"
colnames(ce_1[[1]])[10] <- "Interaction"
ce_1[[1]][10]<- ce_1[[1]][10]+1
#Order levels
#fixing label
d_5_1$guild <- as.character(d_5_1$guild)
d_5_1$guild[d_5_1$guild=="Bee"] <- "Bees"
ce_1[[1]]$guild <- as.character(ce_1[[1]]$guild)
ce_1[[1]]$guild[ce_1[[1]]$guild=="Bee"] <- "Bees"

@@

  theme_bw()+ ylab("Nº of visits per plant taxa") + xlab("Plant reproductive groups")+

@@

>>>>

setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github
m_5_clust_zero_neg_hclust <- readRDS("model_forest_data.RDS")
setwd("~/R_Projects/Reproductive Traits")
d_5_1 <- read.csv("Data/Csv/d_5_1_brms_all_5_clusters.csv")
#Visits
ce_1 <- conditional_effects(m_5_clust_zero_neg_hclust, effects = "Clusters:guild",points=T) 
#change colnames in model output to use same aesthetics
#if not gg seems to don't like it
colnames(ce_1[[1]])[4] <- "a"
colnames(ce_1[[1]])[10] <- "Interaction"
ce_1[[1]][10]<- ce_1[[1]][10]+1
#Order levels
#fixing label
d_5_1$guild <- as.character(d_5_1$guild)
d_5_1$guild[d_5_1$guild=="Bee"] <- "Bees"
ce_1[[1]]$guild <- as.character(ce_1[[1]]$guild)
ce_1[[1]]$guild[ce_1[[1]]$guild=="Bee"] <- "Bees"

@@

  theme_bw()+ ylab("Nº of visits per plant taxa") + xlab("Plant functional groups")+

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=9, fig.width=13}
library(ggplot2)
library(brms)
library(png)
library(grid)
library(grid)
library(gridExtra)

setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github
model_forest_data <- readRDS("model_forest_data.RDS")
setwd("~/R_Projects/Reproductive Traits")
d_5_1 <- read.csv("Data/Csv/d_5_1_brms_all_5_clusters.csv")
#Visits
ce_1 <- conditional_effects(model_forest_data, effects = "Clusters:guild",points=T) 
#change colnames in model output to use same aesthetics
#if not gg seems to don't like it
colnames(ce_1[[1]])[4] <- "a"
colnames(ce_1[[1]])[10] <- "Interaction"
ce_1[[1]][10]<- ce_1[[1]][10]+1
ce_1[[1]][12]<- ce_1[[1]][12]+1
ce_1[[1]][13]<- ce_1[[1]][13]+1

ce_1[[1]]$guild <- as.character(ce_1[[1]]$guild)

ce_1[[1]]$guild[ce_1[[1]]$guild=="Bee"] <- "Bees"
#Order levels
ce_1[[1]]$guild <- factor(ce_1[[1]]$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera","Other_insects"))
d_5_1$guild <- factor(d_5_1$guild, levels = c("Bees","Non-bee-Hymenoptera","Syrphids","Non-syrphids-diptera","Lepidoptera","Coleoptera","Other_insects"))
#plot model
ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(guild), group = 
                        as.factor(guild))) +
  geom_point(size = 1.2, position = position_dodge(width = 0.8), alpha=1) +
  theme_bw()+ ylab("Nº of visits per plant taxa") + xlab("Plant reproductive groups")+
  geom_errorbar(data=ce_1[[1]],mapping=aes(x=Clusters, ymin=lower__, ymax=upper__,colour = as.factor(guild), group = 
                                             as.factor(guild)), width=.6,alpha=0.8, size = 0.9,position = position_dodge(width = 0.8)) +
  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black","grey"))+ylim(0,30)
